Towards Comparable Active Learning

### 2023-05-24 doc/al_benchmark_paper.tex
mnist dataset

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overview}
Table \ref{tab:benchmark_comparison} shows a feature comparison between our proposed benchmark and several existing benchmarks in the literature, as well as methodological AL papers with an extensive experiments section. \\
{\color{red} TODO} We include in this table any methodological paper that experiments on at least two domains. \\
{\color{red} TODO} Define AL scenarios (really hard)
\begin{table}[h]
	\centering
	\begin{tabular}{l | c c c c c}
		Paper & \# Datasets & Domains & Scenarios & Oracle & RL Alg. \\
		\hline
		Beck et al. \cite{beck2021effective} & 4 & 1 & 3 & - & - \\
		Hu et al. \cite{hu2021towards} & 5 & 2 & 1 & - & - \\
		Li et al. \cite{li2022empirical} & 5 & 1 & 1 & - & - \\
		Zhou et al. \cite{zhou2021towards} & 3 & 2 & 1 & \checkmark & - \\
		\textbf{Ours} & 5 & 2 & 2 & \checkmark & -
	\end{tabular}
	\caption{Comparison of our benchmark with the existing literature}
	\label{tab:benchmark_comparison}
\end{table}

@@

@@

\section{Hyperparameters per Dataset}\label{app:hyperparameters}
\begin{table}[H]
	\centering
	\begin{tabular}{l || l | l l l l}
		Dataset & Classifier & Optimizer & LR & Weight Decay & Dropout \\
		\hline
		Splice & [24, 12] & NAdam & 1.2e-3 & 5.9e-5 & 0 \\
		SpliceEnc. & [12, 48] & NAdam & 6.2e-4 & 5.9e-6 & 0 \\
		DNA & [24, 12] & NAdam & 3.9e-2 & 3.6e-5 & 0 \\
		DNAEnc & [24] & NAdam & 1.6e-3 & 4e-4 & 0 \\
		USPS & [24, 12] & Adam & 8.1e-3 & 1.5e-6 & 0 \\
		USPS & [48, 24] & NAdam & 7.8e-3 & 1.9e-6 & 0 \\
		FashionMnist & ResNet18 & NAdam & 1e-3 & 0 & 0 \\
		FashionMnistEnc & linear & Adam & 1.6e-3 & 1e-5 & 5e-2 \\
		Cifar10 & ResNet18 & NAdam & 1e-3 & 0 & 0 \\
		Cifar10Enc & linear & NAdam & 1.7e-3 & 2.3e-5 & 0 \\
		TopV2 & BiLSTM & NAdam & 1.5e-3 & 1.7e-7 & 5e-2 \\
		News & BiLSTM & NAdam & 1.5e-3 & 1.7e-7 & 5e-2 \\
	\end{tabular}
	\caption{Classifier architectures and optimized hyperparameters per dataset. Numbers in brackets signify a MLP with corresponding hidden layers.}
	\label{tab:architectures}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overview}
Table \ref{tab:benchmark_comparison} shows a feature comparison between our proposed benchmark and several existing benchmarks in the literature, as well as methodological AL papers with an extensive experiments section. \\
{\color{red} TODO} We include in this table any methodological paper that experiments on at least two domains.
\begin{table}[h]
	\centering
	\begin{tabular}{l | c c c c c}
		Paper & Sampling & \# Datasets & Domains & Algorithms & Oracle \\
		\hline
		Beck et al. \cite{beck2021effective} & batch & 4 & 1 & 7 & - \\
		Hu et al. \cite{hu2021towards} & batch & 5 & 2 & 13 & - \\
		Li et al. \cite{li2022empirical} & batch & 5 & 1 & 13 & - \\
		Zhou et al. \cite{zhou2021towards} & batch & 3 & 2 & 2 & \checkmark \\
		\textbf{Ours} & single & 9 & 4 & 6 & \checkmark 
	\end{tabular}
	\caption{Comparison of our benchmark with the existing literature}
	\label{tab:benchmark_comparison}
\end{table}

@@

\section{Limitations and Future Work}
No batch AL \\
No learned algorithms \\
No improved classifier training (semi-supervised, etc.)

@@

\section{Hyperparameters per Dataset}\label{app:hyperparameters}
\begin{table}[H]
	\centering
	\begin{tabular}{l || l | l l l l}
		Dataset & Classifier & Optimizer & LR & Weight Decay & Dropout \\
		\hline
		Splice & [24, 12] & NAdam & 1.2e-3 & 5.9e-5 & 0 \\
		SpliceEnc. & linear & NAdam & 6.2e-4 & 5.9e-6 & 0 \\
		DNA & [24, 12] & NAdam & 3.9e-2 & 3.6e-5 & 0 \\
		DNAEnc & linear & NAdam & 1.6e-3 & 4e-4 & 0 \\
		USPS & [24, 12] & Adam & 8.1e-3 & 1.5e-6 & 0 \\
		USPS & linear & NAdam & 7.8e-3 & 1.9e-6 & 0 \\
		FashionMnist & ResNet18 & NAdam & 1e-3 & 0 & 0 \\
		FashionMnistEnc & linear & Adam & 1.6e-3 & 1e-5 & 5e-2 \\
		Cifar10 & ResNet18 & NAdam & 1e-3 & 0 & 0 \\
		Cifar10Enc & linear & NAdam & 1.7e-3 & 2.3e-5 & 0 \\
		TopV2 & BiLSTM & NAdam & 1.5e-3 & 1.7e-7 & 5e-2 \\
		News & BiLSTM & NAdam & 1.5e-3 & 1.7e-7 & 5e-2 \\
	\end{tabular}
	\caption{Classifier architectures and optimized hyperparameters per dataset. Numbers in brackets signify a MLP with corresponding hidden layers.}
	\label{tab:architectures}
\end{table}
